Multi-Robot Probabilistic Mapping and Exploration

### 2018-06-26 Dissertation/Thesis/tex/ae2D.tex
finished editing chap. 4

Similar to the expanding ring approach, $n_c$ candidate pose locations are considered, where those violating \refeqn{CollisionInequalityConstraint} are neglected from further consideration. However, unlike the ring expanding approach, the candidates have different distances from the robot in general, so the objective function is modified to enforce a cost on the squared distance from the current pose location $x_t$ to the candidate location $x_c$, i.e.,
\begin{align}
\label{eqn:ObjFunApproxCompleteCartesian}
\mathcal I(x_c,R_c^*,x_t)\approx \sum_{z_{c,i}\in R_{c}^*\text{ FOV}}\bigg(H(P(m))-\text{E}\left[H(P(m|x_c,z_{c,i}))\right]\bigg)-k_\text{dist}(x_t-x_c)^\T(x_t-x_c),
\end{align}
where weighting function $k_\text{dist}$ represents the sensitivity to avoiding large motions across the map. Furthermore, the same candidate locations are considered throughout the repeated processes of exploration, and the map cell occupancies are assumed static. Therefore, if candidate location $x_c$ fails to satisfy $\mathcal I(x_c,R_c^*,x_t)+k_\text{dist}(x_t-x_c)^\T(x_t-x_c)\geq\mathcal I_\text{min}$, then $x_c$ need \emph{never} be considered again. Avoiding these unnecessary calculations yields a greatly lowered computational burden, particularly late in exploration where several regions are collision-free but disadvantageous to revisit.

>>>>

Similar to the expanding ring approach, $n_c$ candidate pose locations are considered, where those violating \refeqn{CollisionInequalityConstraint} are neglected from further consideration. However, unlike the ring expanding approach, the candidates have different distances from the robot in general, so the objective function is modified to enforce a cost on the squared distance from the current pose location $x_t$ to the candidate location $x_c$, i.e.,
\begin{align}
\label{eqn:ObjFunApproxCompleteCartesian}
\mathcal I(x_c,R_c^*,x_t)\approx \sum_{z_{c,i}\in R_{c}^*\text{ FOV}}\bigg(H(P(m))-\text{E}\left[H(P(m|x_c,z_{c,i}))\right]\bigg)-k_\text{dist}\norm{x_t-x_c}^2,
\end{align}
where weighting function $k_\text{dist}$ represents the sensitivity to avoiding large motions across the map. Furthermore, the same candidate locations are considered throughout the repeated processes of exploration, and the map cell occupancies are assumed static. Therefore, if candidate location $x_c$ fails to satisfy $\mathcal I(x_c,R_c^*,x_t)+k_\text{dist}\norm{x_t-x_c}^2\geq\mathcal I_\text{min}$, then $x_c$ need \emph{never} be considered again. Avoiding these unnecessary calculations yields a greatly lowered computational burden, particularly late in exploration where several regions are collision-free but disadvantageous to revisit.

### 2018-06-26 Dissertation/Thesis/tex/ae3Dsimple.tex
finished editing chap. 4

\subsubsection{Collision and Entropy Maps}
Occupancy grid map cell volume is frequently smaller than the size of the robot taking measurements, particularly with highly-detailed maps. This motivates a method to simply represent locations that risk collision, referred to as a \emph{collision map} $C$. Let $k_C\geq1$ be an integer representing the minimum number of 3D grid cells that form a cube that can completely encompass the robot, i.e., the collision map cell edge length is
\begin{align}
\label{eqn:alphaC}
\alpha_C=k_C\alpha.
\end{align}
Consider the set $m_{C,k}\subset m$ consisting of the 3D grid cells falling inside the limits of the $k$-th cell of collision map $C$, namely $\mathbf{C}_k$. Then the collision probability is
\begin{align}
P(\mathbf{C}_k)=\max{(P(\mathbf{m}_i)\ \forall \ i\in m_{C,k})}.
\end{align}
Then, the robot is only allowed to consider moving into $k$-th cell of the collision map if
\begin{align}
P(\mathbf{C}_k) \leq C_\text{thresh},
\end{align}
where $C_\text{thresh}>0$ is a maximum acceptable collision threshold, typically chosen slightly greater than $0$. In short, this conservative approach limits robotic motion to regions with a low risk of collision while neglecting objects far above or below the exploration plane.

In a similar method, \emph{entropy map} $E$ determines cells based on the entropy metric of \refeqn{ShannonsEntropyCell} over a different subset of cells. Let the $E$ be a 2D map composed of cells with edge length $\alpha$ located at the exploration height. Let the set $m_{E,k}\subset m$ be the cells directly above and below the $k$-th cell of $E$, neglecting any 3D cells located lower than the floor height. Selecting this set is advantageous because measurements are assumed not to penetrate occupied cells (edge length $\alpha$) and measurement rays are typically not closely-aligned with the third axis of the inertial frame (vertically long set). Furthermore, any cells located below the floor, which cannot be reached, should not impact the uncertainty of the space. Then, the occupancy probability of the $k$-th entropy map cell is selected as
\begin{align}
\label{eqn:ProbEntropyMap}
P(\mathbf{E}_k)=\argmax_{P(\mathbf{m}_i)}(H(P(\mathbf{m}_i))\ \forall \ i\in m_{E,k}).
\end{align}
After several measurements of the cells belonging to $m_{E,k}$, it is common for $H(P(\mathbf{E}_k))\approx0$, which implies that these cells are well-known. However, this does not imply that the captured space is \emph{entirely} free or occupied (e.g. an object on the ground that does not breach the upper map boundary), so applying \refeqn{ProbEntropyMap} alone could arbitrarily set $P(\mathbf{E}_k)$ close to $0$ or $1$. This can have damaging effects on the expected information of cells beyond the $k$-th cell. Let $P_\text{min}>0$ be a lower bound such that $H(P_\text{min})=H(1-P_\text{min})\approx0$. If $H(P(\mathbf{E}_k))\leq H(P_\text{min})$, then this probability is corrected to
\begin{align}
P(\mathbf{E}_k)= 
\begin{cases}
    P_\text{min},			& \text{if } \text{mean}(P(\mathbf{m}_i)\ \forall \ i\in m_{E,k})\leq0.5\\
    1-P_\text{min},              & \text{otherwise}
\end{cases},
\end{align}
where the first case corresponds to mostly open space and the second case corresponds to mostly occupied space (e.g. walls and objects). In short, the candidates are only considered if they can be reached over collision map $C$ via Dijkstra's search, and the information gains of the reachable candidates are predicted using entropy map $E$.

\subsubsection{Collision and Entropy Combination Map}
The second proposed technique combines the advantages of both the collision and entropy maps into a 2D projected occupancy grid map, which can be used for both tasks. Let the \emph{collision and entropy combination map} $B$ be a 2D projected map located at the exploration height with grid cell edges the same as the collision map, namely $\alpha_C$ from \refeqn{alphaC}, using the same subset of grid cells from the collision map, namely $m_C$. Considering that the cells begin with uniform probability $P_\text{init}$ where $0<P_\text{init}<1$, define a threshold $P_\text{thresh}$ such that $P_\text{init}<P_\text{thresh}<1$. Then, the probability assigned to the $k$-th grid cell of $B$ is
\begin{align}
P(\mathbf{B}_k)= 
\begin{cases}
    P(\mathbf{C}_k),			& \text{if }P(\mathbf{C}_k)\geq P_\text{thresh}\\
    \min{(P(\mathbf{m}_i)\ \forall \ i\in m_{C,k})},              & \text{otherwise}
\end{cases}.
\end{align}

This approach has several advantages. First, measurements must enter the vicinity of the $k$-th cell for $P(\mathbf{B}_k)$ to change from $P_\text{init}$. Without prior measurements, capturing $P(\mathbf{B}_k)$ produces a large reward for the expected information gain in \refeqn{ObjFun}. Second, the value of $P_\text{thresh}$ can be modified based on how conservative the collision risk assessment for a robot should be. Additionally, when $P(\mathbf{B}_k)<P_\text{thresh}$, this event tends to favor free cells such that expected information gains of cells beyond the $k$-th cell have greater impact on exploration. Furthermore, a single map is simpler, and since cell sizes satisfy $\alpha_C\geq\alpha$, it follows that $n_r$ can only be decreased with $\alpha_C$, thereby increasing computational speed.

@@

The following numerical example involves a simulated quadrotor taking measurements of a large room and generating a 3D occupancy grid map. Both types of map projections are used for autonomous exploration.

@@

Using fixed transforms between the quadrotor body and its onboard sensors, an original mapping node uses a variation of ROS message filters, known as transform message filters, to synchronize the sensor poses with sensor readings. These serve as inputs for ray casting in 3D, which provides the cell probabilities and depths along the ray through geometry. Then, the inverse sensor model serves to update the map ray-by-ray.  The node is designed to work for any number of sensors, specified by sensor parameters in a yaml configuration file.

There are two processes for exploration. The first process is projecting the 3D map onto 2D maps; the same code under different conditional parameters produces two nodes, for collision and entropy maps. The second process subscribes to these two 2D maps; the collision map serves as input for candidate pose consideration and Dijkstra's search, and the entropy map serves to predict information gain. This node provides path messages, composed of desired poses $0.01$sec apart, displayed with a ROS visualization package, Rviz.

@@

The 3D mapping and exploration algorithms are simulated with several parameters.  In particular, the Xtion and Hokuyo are modeled using normalized Gaussian and uniform distributions for the sensor model, with a Gaussian probability of $0.9$ with $\sigma_\text{Xtion}=0.25$m and $\sigma_\text{Hokuyo}=0.1$m, respectively, which are greater than their specified values to account for pose uncertainty and distortion with the Xtion. Since the Xtion tends to distort depths significantly beyond $4$m, this maximum reading considered for both the Xtion and Hokuyo, and the uniform distribution (probability $0.1$) covers the sensor ranges from $0.5$m to $4$m. A cell size of $\alpha=0.075$m is selected and the map limits are $-4$m to $4$m in the x-direction, $-6$m to $6$m in the y-direction, and $-0.15$m to $1.5$m in the z-direction. The initial probability of cells is selected at $P_\text{init}=0.1$. For the collision map, the cell edge factor is $k_C=3$. Additionally, Dijkstra's algorithm produces a cost map composed of distance costs for each collision map cell, denoted $d_\text{cell}$, from the current robot position to the candidate pose locations over a collision-free path about the occupancy grid. A normalized variation on the \emph{bump function}~\cite{Joh06} with maximum distance $d_\text{max}>0$,% TODO: CHECK!
\begin{align}
\label{eqn:bumpFun}
\text{bump}(d_\text{cell})= 
\begin{cases}
    e^{1-\frac1{1-(d_\text{cell}/d_\text{max})^2}},			& \text{if }-d_\text{max}<d_\text{cell}<d_\text{max}\\
    0,              				& \text{otherwise}
\end{cases},
\end{align}
is multiplied to \refeqn{ObjFunApproxCompleteCartesian} in place of the Euclidean cost term, namely $k_\text{dist}(x_t-x_c)^\T(x_t-x_c)$, which is removed. For this experiment, $d_\text{max}$ is chosen as the maximum value of $d_\text{cell}$ on the cost map. This serves to prioritize understanding the local surrounding space before the robot moves across the map to distant regions, while still considering all of the pose candidates.

In the simulation, the robot explores the simulated environment for $8$min while taking measurements. The 3D occupancy grid map and true environment are shown in Figure \ref{fig:sim3DMap}. The Gazebo simulated environment and two 2D projected maps for collision and entropy are shown in Figure \ref{fig:sim2Dmaps}. The total map entropy as a function of time is shown in Figure \ref{fig:simH}.

\begin{figure}[!t]
    	\begin{subfigure}[t]{0.24\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_1min.jpg}
        		\caption{$t=1$min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.24\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_2min.jpg}
        		\caption{$t=2$min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.24\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_3min.jpg}
        		\caption{$t=3$min}
   	\end{subfigure}
    	\begin{subfigure}[t]{0.24\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_4min.jpg}
        		\caption{$t=4$min}
    	\end{subfigure}
	\begin{subfigure}[t]{0.24\columnwidth}
	\vspace*{0.15\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_5min.jpg}
        		\caption{$t=5$min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.24\columnwidth}
	\vspace*{0.15\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_6min.jpg}
        		\caption{$t=6$min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.24\columnwidth}
	\vspace*{0.15\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_7min.jpg}
        		\caption{$t=7$min}
   	\end{subfigure}
    	\begin{subfigure}[t]{0.24\columnwidth}
	\vspace*{0.15\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_8min.jpg}
        		\caption{$t=8$min}
    	\end{subfigure}
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
\caption{Simulated 3D Occupancy Grid Map}
\label{fig:sim3DMap}
\end{figure}

\begin{figure}
	\centering
	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[height=1.5\textwidth]{gazebo_view.png}
        		\caption{Environment}
    	\end{subfigure}
		\hspace*{0.05cm}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim = {3.6cm 17cm 52.5cm 4cm}, clip, height=1.5\textwidth]{gazebo_4min.jpg}
        		\caption{Collision Map}
    	\end{subfigure}
	\hspace*{0.1cm}
	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim = {18cm 17cm 38.1cm 4cm}, clip, height=1.5\textwidth]{gazebo_4min.jpg}
        		\caption{Entropy Map}
		\label{fig:sim2DmapsC}
    	\end{subfigure}
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
\caption{Simulated Environment and 2D Projected Maps at $4$min}
\label{fig:sim2Dmaps}
\end{figure}

@@

The two-map approach exhibits advantages and disadvantages. The exploration algorithm successfully avoided collisions and gave way to a fairly complete 3D occupancy grid. The floor, which is not always visible, is properly estimated in most places. Conversely, this attention to detail has negative consequences that encourage the robot to repeatedly look at the same regions from different vantage points.
Since an entropy map cell is composed from many 3D grid cells single-stacked vertically, if just one of these 3D map cells is not captured or hardly captured, the entropy map cell will be recorded as quite uncertain, shown covering numerous locations in Figure \ref{fig:sim2DmapsC}. The robot may attempt to measure this space again, even when other regions might more strongly warrant observation. These periods of sluggish entropy decrease are shown with flatter sections of Figure \ref{fig:simH}. In short, this algorithm successfully explores the space collision-free while producing a complete map, but over-attention to just a few uncertain cells has negative consequences on the exploration speed.

>>>>

\subsubsection{Collision and Entropy Maps}
Occupancy grid map cell volume is frequently smaller than the size of the robot taking measurements, particularly with highly-detailed maps. This motivates a method to simply represent locations that risk collision, referred to as a \emph{collision map} $C$. Let $k_C\geq1$ be an integer representing the minimum number of 3D grid cells that form a cube that can completely encompass the robot, i.e., the collision map cell edge length is
\begin{align}
\label{eqn:alphaC}
\alpha_C=k_C\alpha.
\end{align}
Consider the set $ m_{C,k}\subset m$ consisting of the 3D grid cells falling inside the limits of the $k$-th cell of collision map $C$, namely $\mathbf{C}_k$. Then the collision probability is
\begin{align}
P(\mathbf{C}_k)=\max{(P(\mathbf{m}_i)\ \forall \ i\in m_{C,k})}.
\end{align}
Then, the robot is only allowed to consider moving into $k$-th cell of the collision map if
\begin{align}
P(\mathbf{C}_k) \leq C_\text{thresh},
\end{align}
where $C_\text{thresh}>0$ is a maximum acceptable collision threshold, typically chosen slightly greater than $0$. In short, this conservative approach limits robotic motion to regions with a low risk of collision while neglecting objects far above or below the exploration plane.

In a similar method, \emph{entropy map} $E$ determines cells based on the entropy metric of \refeqn{ShannonsEntropyCell} over a different subset of cells. Let the $E$ be a 2D map composed of cells with edge length $\alpha$ located at the exploration height. Let the set $ m_{E,k}\subset m$ be the cells directly above and below the $k$-th cell of $E$, neglecting any 3D cells located lower than the floor height. Selecting this set is advantageous because measurements are assumed not to penetrate occupied cells (edge length $\alpha$) and measurement rays are typically not closely-aligned with the third axis of the inertial frame (vertically long set). Furthermore, any cells located below the floor, which cannot be reached, should not impact the uncertainty of the space. Then, the occupancy probability of the $k$-th entropy map cell is selected as
\begin{align}
\label{eqn:ProbEntropyMap}
P(\mathbf{E}_k)=\argmax_{P(\mathbf{m}_i)}(H(P(\mathbf{m}_i))\ \forall \ i\in m_{E,k}).
\end{align}
After several measurements of the cells belonging to $ m_{E,k}$, it is common for $H(P(\mathbf{E}_k))\approx0$, which implies that these cells are well-known. However, this does not imply that the captured space is \emph{entirely} free or occupied (e.g. an object on the ground that does not breach the upper map boundary), so applying \refeqn{ProbEntropyMap} alone could arbitrarily set $P(\mathbf{E}_k)$ close to $0$ or $1$. This can have damaging effects on the expected information of cells beyond the $k$-th cell. Let $P_\text{min}>0$ be a lower bound such that $H(P_\text{min})=H(1-P_\text{min})\approx0$. If $H(P(\mathbf{E}_k))\leq H(P_\text{min})$, then this probability is corrected to
\begin{align}
P(\mathbf{E}_k)= 
\begin{cases}
    P_\text{min},			& \text{if } \text{mean}(P(\mathbf{m}_i)\ \forall \ i\in m_{E,k})\leq0.5\\
    1-P_\text{min},              & \text{otherwise}
\end{cases},
\end{align}
where the first case corresponds to mostly open space and the second case corresponds to mostly occupied space (e.g. walls and objects). In short, the candidates are only considered if they can be reached over collision map $C$ via Dijkstra's search, and the information gains of the reachable candidates are predicted using entropy map $E$.

\subsubsection{Collision and Entropy Combination Map}
The second proposed technique combines the advantages of both the collision and entropy maps into a 2D projected occupancy grid map, which can be used for both tasks. Let the \emph{collision and entropy combination map} $ m_\text{2D}$ be a 2D projected map located at the exploration height with grid cell edges the same as the collision map, namely $\alpha_C$ from \refeqn{alphaC}, using the same subset of grid cells from the collision map, namely $ m_C$. Considering that the cells begin with uniform probability $P_\text{init}$ where $0<P_\text{init}<1$, define a threshold $P_\text{thresh}$ such that $P_\text{init}<P_\text{thresh}<1$. Then, the probability assigned to the $k$-th grid cell of $ m_\text{2D}$, namely $\mathbf{m}_{\text{2D},k}$ is
\begin{align}
P(\mathbf{m}_{\text{2D},k})= 
\begin{cases}
    P(\mathbf{C}_k),			& \text{if }P(\mathbf{C}_k)\geq P_\text{thresh}\\
    \min{(P(\mathbf{m}_i)\ \forall \ i\in m_{C,k})},              & \text{otherwise}
\end{cases}.
\end{align}

This approach has several advantages. First, measurements must enter the vicinity of the $k$-th cell for $P(\mathbf{m}_{\text{2D},k})$ to change from $P_\text{init}$. Without prior measurements, capturing $P(\mathbf{m}_{\text{2D},k})$ produces a large reward for the expected information gain in \refeqn{ObjFun}. Second, the value of $P_\text{thresh}$ can be modified based on how conservative the collision risk assessment for a robot should be. Additionally, when $P(\mathbf{m}_{\text{2D},k})<P_\text{thresh}$, this event tends to favor free cells such that expected information gains of cells beyond the $k$-th cell have greater impact on exploration. Furthermore, a single map is simpler, and since cell sizes satisfy $\alpha_C\geq\alpha$, it follows that $n_r$ can only be decreased with $\alpha_C$, thereby increasing computational speed.

@@

The following numerical example involves a simulated quadrotor taking measurements of a large room and generating a 3D occupancy grid map. Separate collision and entropy map projections are used for autonomous exploration.

@@

Using fixed transformations between the quadrotor body and its onboard sensors, an original mapping node uses a variation of ROS message filters, known as transform message filters, to synchronize the sensor poses with sensor readings. These serve as inputs for ray casting in 3D, which provides the cell probabilities and depths along the ray through geometry. Then, the inverse sensor model serves to update the map ray-by-ray.  The node is designed to work for any number of sensors, specified by sensor parameters in a yaml configuration file.

There are two processes for exploration. The first process is projecting the 3D map onto 2D maps; the same code under different conditional parameters produces two nodes, for collision and entropy maps. The second process subscribes to these two 2D maps; the collision map serves as input for candidate pose consideration and Dijkstra's search, and the entropy map serves to predict information gain. This node provides path messages, composed of desired poses $0.01$ sec apart, displayed with a ROS visualization package, Rviz.

@@

The 3D mapping and exploration algorithms are simulated with several parameters, described next.

\paragraph{Maps}

A cell size of $\alpha=0.075$ m is selected and the map limits are $-4$ m to $4$ m in the x-direction, $-6$ m to $6$ m in the y-direction, and $-0.15$ m to $1.5$ m in the z-direction. The initial probability of cells is selected at $P_\text{init}=0.1$. For the collision map, the cell edge factor is $k_C=3$. Additionally, Dijkstra's algorithm produces a cost map composed of distance costs for each collision map cell, denoted $d_\text{cell}$, from the current robot position to the candidate pose locations over a collision-free path about the occupancy grid.

\paragraph{Sensors}

Next we describe the key parameters used for mapping and exploration. The inverse sensor model \refeqn{RayISMAnswer}--\refeqn{Unnormalized} relies on the stochastic properties of two sensors, namely an Asus Xtion color IR depth sensor and a Hokuyo LIDAR. The Xtion and Hokuyo sensors are modeled using a modified version of the beam model for range finders~\cite{ThrBurFox05}. This includes uniform distribution for a phantom reading with probability $P_\text{rand}=0.1$ and a Gaussian distribution with probability $P_\text{hit}=0.9$. The Gaussian distribution corresponds to the desired case when the measurement $z$ correctly captures a particular cell at expected distance $\hat{z}$ with standard deviation $\sigma$. The total forward sensor model for the Xtion and Hokuyo is
\begin{align}
%p_\text{total}(z,z_\text{min},z_\text{max},\hat{z},\sigma)&=P_\text{rand}p_\text{rand}(z,z_\text{min},z_\text{max})+P_\text{hit}p_\text{hit}(z,\hat{z},\sigma),
&p_\text{total}=P_\text{rand}p_\text{rand}+P_\text{hit}p_\text{hit},
\\
&p_\text{rand}(z,z_\text{min},z_\text{max})=\frac1{z_\text{max}-z_\text{min}},
\\
&p_\text{hit}(z,\hat{z},\sigma)=\frac1{\sqrt{2\pi\sigma^2}}\exp\braces{\frac{(\hat{z}-z)^2}{{2\sigma^2}}},
\end{align}
such that $z_\text{min}=0.5$ m and $z_\text{max}=4.0$ m for both the Xtion and Hokuyo, and the standard deviations are $\sigma_\text{Xtion}=0.25$ m and $\sigma_\text{Hokuyo}=0.1$ m, respectively, which exceed their specified values to account for localization uncertainty and sensor distortion of the Xtion. These sensors update the probabilities of cubic 3D cells with edge length $\alpha=0.075$ m and initial probability $P_\text{init}=0.1$.

\paragraph{Bump Function}
Dijkstra's algorithm produces a cost map composed of distance costs for each collision map cell, denoted $d_\text{cell}$, from the current robot position to the candidate pose locations over a collision-free path about the occupancy grid. This cost map provides a more accurate travel distance cost than the Euclidean distance used in \refeqn{ObjFunApproxCompleteCartesian} because the cost map can account for obstacles within the environment, which is particularly important to properly analyze long trajectories. Therefore, we replace $k_\text{dist}\norm{x_t-x_c}^2$ from \refeqn{ObjFunApproxCompleteCartesian} with a normalized variation on the \emph{bump function}~\cite{Joh06} with maximum distance $d_\text{max}>0$,
\begin{align}
\label{eqn:BumpFunRef}
\text{bump}(d)= 
\begin{cases}
    \exp\braces{{1-\frac1{1-(d/d_\text{max})^2}}},			& \text{if }0<d<d_\text{max}\\
    0,              				& \text{otherwise}
\end{cases},
\end{align}
such that $d_\text{max}$ is selected as the maximum cost map value. Then, $\text{bump}(d)$ is multiplied to $\sum_{z_{c,i}\in R_{c}^*\text{ FOV}}\bigg(H(P(m))-\text{E}\left[H(P(m|x_c,z_{c,i}))\right]\bigg)$ from \refeqn{ObjFunApproxCompleteCartesian} when finding optimal poses. The bump function prioritizes actions that improve the knowledge of the local surrounding space before distant traversals across the map.

\paragraph{Simulation}

In the simulation, the robot explores the Gazebo environment for $8$ min while taking measurements. The 3D occupancy grid map and true environment are shown in Figure~\ref{fig:sim3DMap}. The Gazebo simulated environment and two 2D projected maps for collision and entropy are shown in Figure~\ref{fig:sim2Dmaps}. The total map entropy as a function of time is shown in Figure~\ref{fig:simH}.

\begin{figure}[!t]
    	\begin{subfigure}[t]{0.24\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_1min.jpg}
        		\caption{$t=1$ min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.24\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_2min.jpg}
        		\caption{$t=2$ min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.24\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_3min.jpg}
        		\caption{$t=3$ min}
   	\end{subfigure}
    	\begin{subfigure}[t]{0.24\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_4min.jpg}
        		\caption{$t=4$ min}
    	\end{subfigure}
	\begin{subfigure}[t]{0.24\columnwidth}
	\vspace*{0.15\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_5min.jpg}
        		\caption{$t=5$ min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.24\columnwidth}
	\vspace*{0.15\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_6min.jpg}
        		\caption{$t=6$ min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.24\columnwidth}
	\vspace*{0.15\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_7min.jpg}
        		\caption{$t=7$ min}
   	\end{subfigure}
    	\begin{subfigure}[t]{0.24\columnwidth}
	\vspace*{0.15\columnwidth}
           	\centering
          	\includegraphics[trim = {41.5cm 17cm 14.3cm 3.8cm}, clip, height=\textwidth]{gazebo_8min.jpg}
        		\caption{$t=8$ min}
    	\end{subfigure}
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
\caption{Simulated 3D Occupancy Grid Map}
\label{fig:sim3DMap}
\end{figure}

\begin{figure}
	\centering
	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[height=1.5\textwidth]{gazebo_view.png}
        		\caption{Environment}
    	\end{subfigure}
		\hspace*{0.05cm}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim = {3.6cm 17cm 52.5cm 4cm}, clip, height=1.5\textwidth]{gazebo_4min.jpg}
        		\caption{Collision Map}
    	\end{subfigure}
	\hspace*{0.1cm}
	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim = {18cm 17cm 38.1cm 4cm}, clip, height=1.5\textwidth]{gazebo_4min.jpg}
        		\caption{Entropy Map}
		\label{fig:sim2DmapsC}
    	\end{subfigure}
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
\caption{Simulated Environment and 2D Projected Maps at $4$ min}
\label{fig:sim2Dmaps}
\end{figure}

@@

The two-map approach both exhibits advantages and disadvantages. The exploration algorithm successfully avoided collisions and gave way to a fairly complete 3D occupancy grid. The floor, which is not always visible, is properly estimated in most places. Conversely, this attention to detail has negative consequences that encourage the robot to repeatedly look at the same regions from different vantage points.
Since an entropy map cell is composed from many 3D grid cells single-stacked vertically, if just one of these 3D map cells is not captured or hardly captured, the entropy map cell will be recorded as quite uncertain, shown covering numerous locations in Figure~\ref{fig:sim2DmapsC}. The robot may attempt to measure this space again, even when other regions might more strongly warrant observation. These periods of sluggish entropy decrease are shown with flatter sections of Figure~\ref{fig:simH}. In short, this algorithm successfully explores the space collision-free while producing a complete map, but over-attention to just a few uncertain cells has negative consequences on the exploration speed.
